test_imputed

### 2016-05-27 finalwriteup/draft.rmd
backwards at work
re-syncing mac draft

In this example, the average area under the curve (AUC) was 0.763 indicating that on the whole, taking into account all possible thresholds, the model is predicting profit/loss better than random chance but not perfectly. 20 models and their resulting AUC statistics from each method were initially determined. These were used to calculate how many models were required to achieve a minimum statistical power of 0.8 when compared to the boosted tree results. The comparison of logistic regression required 100 models, while randomForest required over 700 because the AUC distributions were close. It was decided that randomForest and boosted trees would likely not be distinguishable, and 100 models of each method were created via performing 10 fold cross validation 10 times. The violin plot below summarises the AUC values from each method.

@@

* AUC for random forest, everything else without imputing?? thats what i did
    * boxplot showing AUC for all methods. how many runs, 20?
* only take best performing models and try with imputed data

* imputing - boosted trees still fine
    * apply to other methods

* boxplot chart showing AUC's for all methods on one plot : )

* table showing significance p value numbers - in comparison to what? the best performing one?

>>>>

In this example, the average area under the curve (AUC) was 0.763 indicating that on the whole, taking into account all possible thresholds, the model is predicting profit/loss better than random chance but not perfectly. 20 models and their resulting AUC statistics from each method were initially determined. These were used to calculate how many models were required to achieve a minimum statistical power of 0.8 when compared to the boosted tree results. The comparison of logistic regression required 100 models, while randomForest required over 700 because the AUC distributions were close. It was decided that randomForest and boosted trees would likely not be distinguishable, and 100 models of each method were created via performing 10 fold cross validation 10 times. The violin plot below summarises the AUC values from each method. The 'violins' are coloured according whether the distributions significantly vary to boosted trees using a critical value of 0.05.

@@

The performance of logistic regression and random forest algorithms cannot be statistically differntiated from boosted trees. The same process was repeated using an imputed dataset. Imputation was done using the MICE package and allowed all algorithms to be trialled with a full dataset. Again, 100 models were required to achieve a power of 0.8 although this could not be achieved for random forest unless over 450000 models were made.

```{r mice_violin}

```{r all_violin}

Imputed data tightens the distribution of randomForest substantially but slightly spreads the distriution of Boosted trees and logistic regression.

### 2016-05-27 rf_log_naiive_auc.rmd
re-syncing mac draft

setwd("C:/Users/n9232371/Documents/Consultbusiness/data")

all10mice<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all10mice.csv')[,-1]
all10rf<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all10rf.csv')[,-1]
all9c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all9c.csv')[,-1]
all9a<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all9a.csv')[,-1]

@@

all10a<- all9c %>% select(no.users, Discipline, pc.pro, Business,
                         b.timespan.cbrt, inv.mlsto.log, client.totinv.log, 
                         mlsto, Year, b.rpdol)
all10a<- all10a[complete.cases(all10a),]
# 2280 cases - 10 vars

all10b<- all9c %>% select(no.users, Discipline, pc.pro, Business,
                         b.timespan.cbrt, inv.mlsto.log, client.totinv.log, 
                         mlsto, Year, b.rpdol, majority.pos, pc.majpos.log)
all10b<- all10b[complete.cases(all10b),]
# 1987 cases - 12 vars

all10c<- all9c %>% select(no.users, Discipline, pc.pro, Business, JD.Second,
                         b.timespan.cbrt, inv.mlsto.log, client.totinv.log, 
                         mlsto, Year, b.rpdol, majority.pos, pc.majpos.log)
all10c<- all10c[complete.cases(all10c),]
# 1106 cases - 13 vars

@@

        for(i in 1:length(dfs)){
                df = get(df.list[i])

@@

                } else{
                if(nrow(df) <= 2300){
                        # include code.client, code.contact, Billing.Type
                        formula<- "f.rpdol ~ . -Year -b.rpdol -inv.mlsto.log - return.pdol - timespan.cbrt - mlsto"
                }
                }

@@

@@

                        } else {
                                if(method %in% 'log'){
                                        fit<- glm(as.formula(formula), 
                                                  data = df[-folds[[j]],], family = binomial())
                                        pred <- predict(fit, test,
                                                        type = "response")
                                } else {
                                        fit <- gbm(as.formula(formula), data = df[-folds[[j]],],
                                                   distribution = "bernoulli", n.trees = 10000,
                                                   shrinkage = 0.001, interaction.depth = 5,
                                                   n.minobsinnode = 20)

                                                pred <-predict(fit, test, 
                                                               n.tree = 10000, type = "response")
                                                }
                        }

@@

                        auc[[i]][j]<- auc(pred.p)

@@

df.list <- c("all10rf", "all10mice", "all10a", "all10b", "all10c")
test.roc(dfs = df.list, seed = 400, mtrys = c(4,5,3,4,4), method = "log")
ggplot(melt(auc.func), aes(x= factor(L1), y= value)) + geom_boxplot() + geom_point() +
        stat_summary(fun.y="mean", geom="point", colour = "red")

@@

@@

df = all10mice

@@

Checking p value for BN

```{r}
reduc.totAUC <- readRDS("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/reduc_df_auc.rds")
BN = read.csv("C:/Users/n9232371/Documents/github/consult/finalwriteup/report_data/BN_AUCs.csv")

n.samples(data = list(reduc.totAUC[[2]][1:20], BN$AUC), type.calc = 'two.sample', alt = 'two.sided')

# only 5 samples required according to power calculation

@@

>>>>

setwd("C:/Users/n9232371/Documents/Consultbusiness/data")
setwd("~/OneDrive/shared files/Bligh Tanner/masters/data")

all10mice<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all10mice.csv')[,-1]
all10rf<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all10rf.csv')[,-1]
all9c<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all9c.csv')[,-1]
all9c<- read.csv('all9c.csv')[,-1]
all9a<- read.csv('C:/Users/n9232371/Documents/Consultbusiness/data/all9a.csv')[,-1]

@@

all10a<- all9c %>% select(no.users, Discipline, pc.pro, Business,
                         b.timespan.cbrt, b.inv.log, client.totinv.log, 
                         mlsto, Year, b.rpdol)
all10a<- all10a[complete.cases(all10a),]
# 2280 cases - 10 vars

all10b<- all9c %>% select(no.users, Discipline, pc.pro, Business,
                         b.timespan.cbrt, b.inv.log, client.totinv.log, 
                         mlsto, Year, b.rpdol, majority.pos, pc.majpos.log)
all10b<- all10b[complete.cases(all10b),]
# 1987 cases - 12 vars

all10c<- all9c %>% select(no.users, Discipline, pc.pro, Business, JD.Second,
                         b.timespan.cbrt, b.inv.log, client.totinv.log, 
                         mlsto, Year, b.rpdol, majority.pos, pc.majpos.log)
all10c<- all10c[complete.cases(all10c),]
# 1106 cases - 13 vars

@@

        for(i in 1:length(dfs)){
                df = get(dfs[i])

@@

                } else{
                if(nrow(df) <= 2300){
                        # include code.client, code.contact, Billing.Type
                        formula<- "f.rpdol ~ . -Year -b.rpdol "
                }
                }

@@

                if(method %in% 'naiive') {
                        formula<- "b.rpdol ~ Discipline + pc.pro + b.timespan.cbrt + no.users + inv.mlsto.log + client.totinv.log + Business + majority.pos + JD.Second + pc.majpos.log + Billing.Type + JD.Second"

@@

                        if(method %in% 'log'){
                                fit<- glm(as.formula(formula), 
                                          data = df[-folds[[j]],], family = binomial())
                                pred <- predict(fit, test,
                                                type = "response")
                        } 
                        if(method %in% 'boost'){
                                fit <- gbm(as.formula(formula), data = df[-folds[[j]],],
                                           distribution = "bernoulli", n.trees = 10000,
                                           shrinkage = 0.001, interaction.depth = 5,
                                           n.minobsinnode = 20)

                                pred <- predict(fit, test, n.tree = 10000, type = "response")
                        }

                        if(method %in% 'naiive'){
                                fit<- naiveBayes( as.formula(formula), df[-folds[[j]],])
                                pred <- predict(fit, test, type = 'raw')
                                pred<- pred[,2]
                        }

@@

                        auc[[i]][j]<- auc(pred.p)
                        names(auc)[[i]] = method

@@

df.list <- c("all10rf", "all10mice", "all10a", "all10b", "all10c")
test.roc(dfs = df.list, seed = 400, mtrys = c(4), method = "log",
         x.folds = 5, extra.var = NULL, mult = 1)
names(auc.func) = df.list
ggplot(melt(auc.func), aes(x= factor(L1), y= value)) + geom_boxplot() + geom_point() +
        stat_summary(fun.y="mean", geom="point", colour = "red")

@@

```{r naiive bayes, echo=FALSE}

@@

df = all10mice
df = all9c

@@

Create loop through each method - 20 models - compile AUC results

```{r}
test.roc(dfs = c('all10a'), seed = 100, mtrys = c(5), method = "log",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc = auc.func

test.roc(dfs = c('all9c'), seed = 100, mtrys = c(5), method = "boost",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc = append(tot.auc,auc.func)

test.roc(dfs = c('all10c'), seed = 100, mtrys = c(4), method = "rf",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc = append(tot.auc,auc.func)

test.roc(dfs = c('all9c'), seed = 100, mtrys = c(4), method = "naiive",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc = append(tot.auc,auc.func)

saveRDS(tot.auc,"~/Documents/github/consult/finalwriteup/report_data/reduc_df_auc.rds")

ggplot(melt(tot.auc), aes(x= factor(L1), y= value)) + geom_violin() + geom_jitter() +
        stat_summary(fun.y="mean", geom="point", colour = "red")

# n.samples function is defined in 'draft.rmd'
index = c(1,3,4)
ns = NULL
for(i in seq_along(index)){
        temp = n.samples(data = tot.auc[c(2, index[i])], type.calc = 'two.sample', alt = 'two.sided')
        ns[i] = temp
}
ns

@@

Re-run with MICE imputed data

```{r}

all10mice_f = read.csv('~/OneDrive/shared files/Bligh Tanner/masters/data/all10mice_May16.csv')

test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(5), method = "log",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc.m = auc.func

test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(5), method = "boost",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc.m = append(tot.auc.m,auc.func)

test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(4), method = "rf",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc.m = append(tot.auc.m,auc.func)

test.roc(dfs = c('all10mice_f'), seed = 100, mtrys = c(4), method = "naiive",
         extra.var = NULL, mult = 10, x.folds = 10)
tot.auc.m = append(tot.auc.m,auc.func)

saveRDS(tot.auc.m,"~/Documents/github/consult/finalwriteup/report_data/mice_df_auc.rds")

ggplot(melt(tot.auc.m), aes(x= factor(L1), y= value)) + geom_violin() + geom_jitter() +
        stat_summary(fun.y="mean", geom="point", colour = "red")

# n.samples function is defined in 'draft.rmd'
index = c(1,3,4)
ns = NULL
for(i in seq_along(index)){
        temp = n.samples(data = tot.auc.m[c(2, index[i])], type.calc = 'two.sample', alt = 'two.sided')
        ns[i] = temp
}
ns
